Notes Dendro Analysis

### 2017-05-08 man/notes_dendro_analysis.Rmd
update dendro analysis

* San Juan: [`./data_raw/dendro_ring/sn_sanjuan_cofecha.OUT`](/data_raw/dendro_ring/sn_sanjuan_cofecha.OUT) 
* Cañar: [`./data_raw/dendro_ring/sn_sanjuan_cofecha.OUT`](/data_raw/dendro_ring/sn_sanjuan_cofecha.OUT)

>>>>

* San Juan: [`./data_raw/dendro_ring/sn_sanjuan/sn_sanjuan_cofecha.OUT`](/data_raw/dendro_ring/sn_sanjuan/sn_sanjuan_cofecha.OUT) 
* Cañar: [`./data_raw/dendro_ring/sn_canar/sn_canar_cofecha.OUT`](/data_raw/dendro_ring/sn_canar/sn_canar_cofecha.OUT)
